--- 
title: "Herramientas Estadísticas para Ciencia de Datos"
author:
  - "Sofía Villers Gómez"
  - "David Alberto Mateos Montes de Oca"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: alberto-mateos-mo/seminario_est_libro
description: "Material para el curso Herramientas Estadíticas para Ciencia de Datos del Seminario de Estadística de la Facultad de Ciencias, Universidad Nacional Autónoma de México"
---

# Bienvenido a Herramientas Estadísticas para Ciencia de Datos {-}

```{r include = FALSE}
# source("common.R")
htmltools::tagList(rmarkdown::html_dependency_font_awesome())
library(tidyverse)
library(devtools)
# library(DT)
```

Primera edición del libro de texto para el curso _Herramientas Estadísticas para Ciencia de Datos_ del Seminario de Estadística de la Facultad de Ciencias.

## Objetivos
Como el título lo indica, a lo largo de este libro se expondrán diferentes modelos estadísticos y sus aplicaciones con un enfoque a Ciencia de Datos.

El objetivo es proveer al lector de las herramientas necesarias para comprender los fundamentos de estos modelos y sus aplicaciones mediante el uso del lenguaje R.

## Estructura

El libro se descompone en dos grandes secciones, una de ellas enfocada a presentar diferentes paquetes de R considerados de gran utilidad para la práctica de Ciencia de Datos, la otra se enfoca en la teoría y aplicación de diferentes modelos.

La estructura del libro sigue el orden en que se imparte la materia en la Facultad de Ciencias sin embargo hemos diseñado los capítulos suficientemente independientes como para ser consultados en el orden de preferencia del lector.

## Detalles técnicos

Este libro fue escrito con [bookdown](http://bookdown.org/) usando [RStudio](http://www.rstudio.com/ide/).

Esta versión fue escrita con:

```{r message = FALSE, warning = FALSE, echo = FALSE}
# needed because new_session is set to true in _bookdown.yml
all_pkgs <- renv::dependencies(path = "DESCRIPTION") %>% 
  pull(Package) 
session <- devtools::session_info(pkgs = all_pkgs)
session$platform
```

## Licencia {-}

This work is licensed under a [Creative Commons Attribution-ShareAlike 4.0 International License](https://creativecommons.org/licenses/by-sa/4.0/).

<center>
<i class="fab fa-creative-commons fa-2x"></i><i class="fab fa-creative-commons-by fa-2x"></i><i class="fab fa-creative-commons-sa fa-2x"></i>
</center>

*This is a human-readable summary of (and not a substitute for) the license.
Please see <https://creativecommons.org/licenses/by-sa/4.0/legalcode> for the full legal text.*

**You are free to:**

- **Share**---copy and redistribute the material in any medium or
  format

- **Remix**---remix, transform, and build upon the material for any
  purpose, even commercially.

The licensor cannot revoke these freedoms as long as you follow the
license terms.

**Under the following terms:**

- **Attribution**---You must give appropriate credit, provide a link
  to the license, and indicate if changes were made. You may do so in
  any reasonable manner, but not in any way that suggests the licensor
  endorses you or your use.
  
- **ShareAlike**---If you remix, transform, or build upon the material, you must distribute your contributions under the same license as the original. 

- **No additional restrictions**---You may not apply legal terms or
  technological measures that legally restrict others from doing
  anything the license permits.

**Notices:**

You do not have to comply with the license for elements of the
material in the public domain or where your use is permitted by an
applicable exception or limitation.

No warranties are given. The license may not give you all of the
permissions necessary for your intended use. For example, other rights
such as publicity, privacy, or moral rights may limit how you use the
material.

```{r include = FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```